Tidal field anisotropy as a tracer of cosmic voids

### 2015-01-10 cosmic_voids.tex
Section 4.3 Watershed transform, done.

Since voids were found in the first compiled galaxy surveys 
they have been identified as one of the most striking features of the
Cosmic Web \citep{Chincarini75,  Gregory78, Einasto80M, Einasto80N,
  Kirshner81, Zeldovich82,Kirshner87, Bond96}. 
However,  due to the large volume extension of void regions ($\sim
5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogues of
voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
through  modern galaxy surveys like the two-degree field Galaxy
Redshift Survey \citep{ Colless01, Colless03} and the Sloan Digital
Sky Survey \citep{York00, Abazajian03}.
This advancement generated a great interest to study voids
observationally during the last decade \citep{Hoyle04, Croton04, Rojas05,
  Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.

On the theoretical side the rough theoretical framework that explains
the origin of voids was stablished in the seminal work of
\citet{Zeldovich70} and refined in the following decades.  
The first detailed theoretical models describing formation, dynamics
and properties of  voids \citep{Hoffman82, Icke84, Bertschinger85,
  Blumenthal92} were  complemented and extended by numerical studies
\citep{Martel90, Regos91, Weygaert93, Dubinski93, Bond96}. 
Currently, the dominant tendency to study voids relies on using data
from N-body simulations. For an extensive compilation of previous 
numerical works we refer the reader to \citet{Colberg08}.

@@

In left panels of Fig. \ref{fig:FA_field} we show the FA field for both 
web schemes over a slide of the simulation. 
From this Figure we can observe that both voids and knots display a highly isotropic
expanding dynamic at their centres, becoming gradually more
anisotropic at outer regions. 
On the other hand the filamentary structure is traced by high FA
values. These characteristics are the key to use the FA as a tracer of
cosmic voids.

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \vspace{0.1 cm}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
  \caption{Left colum. Visual impression of the 
  FA field over a slide of the simulation for each web scheme (T-web, upper 
  panels. V-web, middle panels). 
  Middle column. Components of the Cosmic Web using $\lambda_{th}$
  values that put an upper bound of $FA=0.95$ to voids. Voids
  corresponds with white, sheets to gray, filaments to dark gray and
  knots with black regions. 
  Right column. Sketches the distribution of the catalogued voids by
  our method.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

@@

  \label{fig:L1_correlations}
  \vspace{0.1 cm}

@@

From Figs. \ref{fig:FA_field} and \ref{fig:L1_correlations} we
conclude that the FA is a good tracer of voids as it is almost perfectly
correlated with low values of $\lambda_1$. 
We propose that voids should be composed completely by regions of
FA$<0.95$.
If we increase the values of $\lambda_1$ from its minimum until it
we reach FA$=0.95$ in \ref{fig1:L1_correlations} we find that this
correspond to critical values of $\lambda_{1}^T = 0.265$ and
$\lambda_{1}^V = 0.175$ for the Tweb and Vweb, respectively.
This means that setting $\lambda_{th}$ to either
$\lambda_{1}^T$/$\lambda_{1}^{V}$ automatically produces voids with
all the cells $FA<0.95$.   
The middle column in Fig. \ref{fig:FA_field} shows the web
classification for this choice of $\lambda_{th}$, demonstrating that
it is a sensible choice to define voids.

@@

{\bf Reescribir para describir lo que hace el algoritmo}
This algorithm is parameter-free and does  not require any assumption
on the shape and morphology of voids.  
Although we use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a 
Cartesian mesh for estimating the density and tensor fields, instead of 
the more sophisticated \textit{Delaunay tessellation for field estimator} 
(\texttt{DTFE}) technique \citep{Schaap00}, our implementation of the 
watershed transform should not be significantly affected as we are 
interested in low density regions where the \texttt{CIC} gives similar 
estimations.

@@

Describing the density profiles of voids is quite important in order to 
compare and match simulation with observational surveys, allowing possible
constrains for different cosmology models \SRKED{[Hamaous, et.al 2014]}. 
Here, and taking into account the previous results, we rather use an 
ellipsoidal approximation to describe and fit the shape of bulk voids, so 
we use the next ellipsoidal radial coordinate to describe density profiles.

%.........................................................................
%Ellipsoidal radial coordinate
\eq{radial_coordinate}
{
r^2 = \frac{x^2}{\tau_1^2} + \frac{y^2}{\tau_2^2} + \frac{z^2}{\tau_3^2},
\ \ \ \ 0\leq r \leq 1
}
%.........................................................................
where we take the principal moments of inertia $\{\tau_i \}$ as the 
lengths of the principal axes of the ellipsoid and each one of the 
cartesian coordinates as measured in the rotated frame of each void.

We use the same analytic density profile that \SRKED{[Hamaous, et.al 2014]} 
to fit the numerical density profiles of our voids.

%.........................................................................
%Density profile
\eq{density_profile}
{
\delta_v(r) = \delta_c\frac{1-(r/r_s)^\alpha}{1+(r/r_v)^\beta}
}
%.........................................................................

@@

  \captionof{figure}{\small Volume functions of voids for both built 
  catalogues. Watershed-Tweb (red curves), Watershed-Vweb (blue curves).
  Continuous lines corresponds with the total number of voids, dot-dashed
  with sub-compensated voids and dashed lines with over-compensated voids. }

>>>>

Since voids were found in the first compiled galaxy surveys 
they have been identified as one of the most striking features of the
Cosmic Web \citep{Chincarini75,  Gregory78, Einasto80M, Einasto80N,
  Kirshner81, Zeldovich82,Kirshner87, Bond96}. 
However,  due to the large volume extension of void regions ($\sim
5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogs of
voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
through  modern galaxy surveys like the two-degree field Galaxy
Redshift Survey \citep{ Colless01, Colless03} and the Sloan Digital
Sky Survey \citep{York00, Abazajian03}.
This advancement generated a great interest to study voids
observationally during the last decade \citep{Hoyle04, Croton04, Rojas05,
  Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.

On the theoretical side the rough theoretical framework that explains
the origin of voids was established in the seminal work of
\citet{Zeldovich70} and refined in the following decades.  
The first detailed theoretical models describing formation, dynamics
and properties of  voids \citep{Hoffman82, Icke84, Bertschinger85,
  Blumenthal92} were  complemented and extended by numerical studies
\citep{Martel90, Regos91, Weygaert93, Dubinski93, Bond96}. 
Currently, the dominant tendency to study voids relies on using data
from N-body simulations. For an extensive compilation of previous 
numerical works we refer the reader to \citet{Colberg08}.

@@

In left panels of Fig. \ref{fig:FA_field} we show the FA field for both 
web schemes over a slide of the simulation. 
From this Figure we can observe that both, voids and knots, display a highly 
isotropic expanding dynamic at their centres, becoming gradually more
anisotropic at outer regions. 
On the other hand the filamentary structure is traced by high FA
values. These characteristics are the key to use the FA as a tracer of
cosmic voids.

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
  \caption{Left colum. Visual impression of the 
  FA field over a slide of the simulation for each web scheme (T-web, upper 
  panels. V-web, middle panels). 
  Middle column. Components of the Cosmic Web using $\lambda_{th}$
  values that put an upper bound of $FA=0.95$ to voids. Voids
  corresponds with white, sheets to gray, filaments to dark gray and
  knots with black regions. 
  Right column. Sketches the distribution of the catalogued voids by
  our method.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

@@

  \label{fig:L1_correlations}

@@

From Figs. \ref{fig:FA_field} and \ref{fig:L1_correlations} we
conclude that the FA is a good tracer of voids as it is almost perfectly
correlated with low values of $\lambda_1$. 
We propose that voids should be composed completely by regions of
FA$<0.95$.
If we increase the values of $\lambda_1$ from its minimum until it
we reach FA$=0.95$ in \ref{fig:L1_correlations} we find that this
correspond to critical values of $\lambda_{1}^T = 0.265$ and
$\lambda_{1}^V = 0.175$ for the Tweb and Vweb, respectively.
This means that setting $\lambda_{th}$ to either
$\lambda_{1}^T$/$\lambda_{1}^{V}$ automatically produces voids with
all the cells $FA<0.95$.   
The middle column in Fig. \ref{fig:FA_field} shows the web
classification for this choice of $\lambda_{th}$, demonstrating that
it is a sensible choice to define voids.

@@

Once established the FA as a good tracer of voids, the next step is to
find individuals voids in the overall distribution. For this purpose, we
use the \textit{watershed transform algorithm} \citep{Beucher79,Beucher93}, 
in which a void is identified as the catching basin of a local minimum of
the FA. The use of this algorithm is advantageous as it is parameter-free 
and does not require any assumption on the shape and morphology of voids.

Previous implementations of this technique as those of \citet{Platen07,
Neyrinck08} have shown remarkable results regarding voids finding, however
they use the density field instead of the FA field. On the other hand, we 
use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a Cartesian mesh for 
estimating the density and tensor fields, instead of the more sophisticated 
\textit{Delaunay tessellation for field estimator} (\texttt{DTFE}) technique 
\citep{Schaap00}, but our implementation of the watershed transform should 
not be significantly affected as we are interested in low density regions 
where the \texttt{CIC} gives similar estimations.

As suggested by \citet{Platen07} and references therein, it is necessary to
apply a threshold merger in order to reduce spurious features and to avoid 
void hierarchization. A natural choice is a threshold of $\delta = -0.8$, 
which means that any ridge between two voids with density below that value
would be removed and the respective voids merged. As we are working with the
FA, the equivalent threshold according to Fig. \ref{fig:L1_correlations} is
$FA = 0.65$. In right panels of Fig. \ref{fig:FA_field} we show the resulting
catalogs of voids for both schemes.

@@

@@

  \captionof{figure}{\small Volume functions of voids for both built 
  catalogs. Watershed-Tweb (red curves), Watershed-Vweb (blue curves).
  Continuous lines corresponds with the total number of voids, dot-dashed
  with sub-compensated voids and dashed lines with over-compensated voids. }
